### 2018-11-30 latex/figurelegends.tex
Changed model and citation for fig 6

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.7\textwidth]{fig_6_unresolved_loop}
  \caption{\textbf{The function of the structurally unresolved loop of NamPT.} Most deuterostomes that possess NamPT and NNMT show a sequence insertion in the N-terminal region of NamPT that has been revealed by multiple sequence alignment of NamPT from different species (A). Coloured circles indicate the enzymes present in the respective species; blue: NamPT and NNMT; black: NamPT, NADA and NNMT; yellow: NamPT and NADA. For a more comprehensive alignment, please see supplementary figure~S1. The structure visualisation of human NamPT (B) is based on a structure prediction by SWISS-MODEL \cite{Arnold2006,Biasini2014} using the model 2H3D of the human NamPT as template \cite{Wang2006}. The inserted region is not resolved in any of currently available crystal structures of NamPT and thus appears to be a flexible loop structure at the surface of the NamPT dimer, coloured in red. Immunofluorescence images (C) show that the localisation of the FLAG-tagged mutant protein lacking the unresolved loop is not changed compared to FLAG-tagged human wildtype NamPT. Both show a heterogeneous nuclear-cytosolic localisation in HeLa S3 cells. \textit{In vitro} measurements using recombinant protein show that the mutant NamPT has a lower activity than the wildtype enzyme (D) and is not activated by ATP (E). Bars in panels D and E that have different letters indicate significant difference of measured values as estimated using a T~test assuming independent samples and significance at $p < 0.05$. (F) Root mean square deviation (RMSD) with respect to initial structure for simulation of NamPT with loop insertion (red) and without loop insertion (blue), respectively. The RMSD values for the entire simulation (in total 1000 ns) show mostly stable structures with small fluctuations related to rare events.}
  \label{fig:unresolved_loop}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.83\textwidth]{fig_6_unresolved_loop}
\end{figure}

\begin{figure}[ht]
  \caption{\textbf{The function of the structurally unresolved loop of NamPT.} Most deuterostomes that possess NamPT and NNMT show a sequence insertion in the N-terminal region of NamPT that has been revealed by multiple sequence alignment of NamPT from different species (A). Coloured circles indicate the enzymes present in the respective species; blue: NamPT and NNMT; black: NamPT, NADA and NNMT; yellow: NamPT and NADA. For a more comprehensive alignment, please see supplementary figure~S1. The structure visualisation of human NamPT (B) is based on a structure prediction by SWISS-MODEL \cite{Arnold2006,Biasini2014} using the model 3DGR of the human NamPT as template \cite{Burgos2009}. The inserted region is not resolved in any of currently available crystal structures of NamPT and thus appears to be a flexible loop structure at the surface of the NamPT dimer, coloured in red. Immunofluorescence images (C) show that the localisation of the FLAG-tagged mutant protein lacking the unresolved loop is not changed compared to FLAG-tagged human wildtype NamPT. Both show a heterogeneous nuclear-cytosolic localisation in HeLa S3 cells. \textit{In vitro} measurements using recombinant protein show that the mutant NamPT has a lower activity than the wildtype enzyme (D) and is not activated by ATP (E). Bars in panels D and E that have different letters indicate significant difference of measured values as estimated using a T~test assuming independent samples and significance at $p < 0.05$. (F) Root mean square deviation (RMSD) with respect to initial structure for simulation of NamPT with loop insertion (red) and without loop insertion (blue), respectively. The RMSD values for the entire simulation (in total 1000 ns) show mostly stable structures with small fluctuations related to rare events.}
  \label{fig:unresolved_loop}
\end{figure}
